Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-16 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:16	10:03:13	(Fri16.Oct)

We use LCA with variations of the Kaiser window, but a comparison to using trigonometric windows will also be provided. We extend Synnev\aa{}g's work by steering all our windows and not just some, and elaborate on the type of Kaiser windows to include and the method of steering. Then the method is applied to experimental data from the 32 element Kongsberg Maritime HISAS 1030 synthetic aperture sonar (SAS), with a 23$^\circ$ transmit angle operating frequency of 100\,kHz and .

>>>>

In this study apply LCA to active sonar imaging. We use variations of the parametric Kaiser window, but also compare it to the trigonometric window function. We extend Synnev\aa{}g's work by steering all our windows and not just some, and demonstrate how LCA's performance is affected by type and number of windows included. Our results are obtained using experimental data from the 32 element Kongsberg Maritime HISAS 1030 synthetic aperture sonar (SAS), which operates at 100\,kHz with with a transmit angle of 23$^\circ$.
